Extracting the Power of Dependent Types

### 2021-09-27 paper.tex
Fixing warnings produced by submission
Make veritucal spacing a bit nicer.

% Updating copyright info, as per latest ACM email
% after copyright transfer.
\copyrightyear{2021}
\acmYear{2021}
\setcopyright{rightsretained}
\acmConference[GPCE '21]{Proceedings of the 20th ACM SIGPLAN International Conference on Generative Programming: Concepts and Experiences}{October 17--18, 2021}{Chicago, IL, USA}
\acmBooktitle{Proceedings of the 20th ACM SIGPLAN International Conference on Generative Programming: Concepts and Experiences (GPCE '21), October 17--18, 2021, Chicago, IL, USA}
\acmDOI{10.1145/3486609.3487201}
\acmISBN{978-1-4503-9112-2/21/10}

@@

\usepackage{todonotes}

@@

% Fixing overfull lines
\emergencystretch=10.0pt % default 0.0pt
\hyphenpenalty=500 % default 50
\exhyphenpenalty=500 % default 50

@@

%% Title information
\title[]{Extracting The Power of Dependent Types}

@@

\begin{acks}
We would like to thank reviewers for their constructive suggestions.
This work is supported by the \grantsponsor{EPSRC}{Engineering and
Physical Sciences Research Council}{https://epsrc.ukri.org} through
the grant \grantnum{EPSRC001}{EP/N028201/1}, and the
\grantsponsor{NWO}{Dutch Research Council}{https://www.nwo.nl/en}
through the grant VI.Veni.202.216.
\end{acks}

>>>>

% Updating copyright info, as per latest ACM email
% after copyright transfer.
\copyrightyear{2021}
\acmYear{2021}
\setcopyright{rightsretained}
\acmPrice{}
\acmConference[GPCE '21]{Proceedings of the 20th ACM SIGPLAN International Conference on Generative Programming: Concepts and Experiences}{October 17--18, 2021}{Chicago, IL, USA}
\acmBooktitle{Proceedings of the 20th ACM SIGPLAN International Conference on Generative Programming: Concepts and Experiences (GPCE '21), October 17--18, 2021, Chicago, IL, USA}
\acmDOI{10.1145/3486609.3487201}
\acmISBN{978-1-4503-9112-2/21/10}

@@

%\usepackage{todonotes}

@@

% Fixing overfull lines
\emergencystretch=2pt % default 0.0pt
\hyphenpenalty=500 % default 50
\exhyphenpenalty=500 % default 50

@@

%% Title information
\title[]{Extracting the Power of Dependent Types}

@@

\begin{acks}
We would like to thank reviewers for their constructive suggestions.
This work is supported by the \grantsponsor{EPSRC}{Engineering and
Physical Sciences Research Council}{https://epsrc.ukri.org} through
the grant

\noindent
\grantnum{EPSRC001}{EP/N028201/1}, and the
\grantsponsor{NWO}{Dutch Research Council}{https://www.nwo.nl/en}
through the grant~VI.Veni.202.216.
\end{acks}
